PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2020-03-31 main.tex
Timescale scaling with dynamical excitation

\noindent Note that a surface density profile with $\alpha < -1$ produces a collision timescale that scales more steeply than the orbital timescale. In this case, an N-body simulation will get more computationally expensive with orbital distance because the time step size scales with the orbital timescale.

@@

>>>>

Note that a surface density profile with $\alpha < -1$ produces a collision timescale that scales more steeply than the orbital timescale. In this case, an N-body simulation will get more computationally expensive with orbital distance because the time step size scales with the orbital timescale.

In terms of encounter velocity, gravitational focusing is the only thing that effects collision timescale. This is because number density of planetesimals $n$ scales with $v^{-1}$, which cancels with the other $v$ term. This leaves us with $t_{coll} \sim v^{2}$ or, in terms of the rms eccentricity (assuming the rms inclination is coupled to the eccentricity)

\begin{equation}
    t_{coll} \sim \left< e^{2} \right>^{1/2}
\end{equation}

@@

In terms of encounter velocity, the relaxation time scales as $t_{relax} \sim v^{4}$. Taking the ratio of the scaling for the collision and relaxation time with rms eccentricity gives (because there is a geometric term in the collision cross section, the ratio of these two timescales still goes as $v^{4}$)

\begin{equation}
    \frac{t_{relax}}{t_{coll}} \sim \left< e^{2} \right>
\end{equation}

Therefore, a dynamically hot disk will have a better chance of inhibiting oligarchic growth. All planetesimal disks will tend toward this state because gravitational stirring is most effective in a cold disk. So long as gas drag does not strongly damp things, this condition could be met. Why doesn't this happen for Kokubo + Ida simulations?
